---
title: "Finding Firms with Largest Delta in Net COVID Sentiment"
output: html_notebook
---



```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(lubridate)
library(corrr)
library(haven)
library(lme4) 
library(broom.mixed) 
library(ggrepel)
library(ggpubr)
library(ggpmisc)
```




Read in data file  

```{r}

firms <- read_dta('../data/firmquarter_2022q1.dta')
firms 

```


Find entries whose COVID Net Sentiment isn't 0

```{r}
NonZero_Firms <- firms |> 
  filter(`Covid_Net_Sentiment` != 0) |> 
  filter(hqcountrycode=='US') |> 
  mutate(Day_of_EarningsCall=dmy(date_earningscall)) 

NonZero_Firms 
```


Find firms (and their earnings calls) the largest Deltas in their Net COVID Sentiments over time.

```{r}

Min_Max_Net_COVID_Sentiments <- NonZero_Firms |> 
  group_by(company_name) |> 
  mutate(Min_Net_COVID_Sentiment=min(Covid_Net_Sentiment)) |> 
  mutate(Max_Net_COVID_Sentiment=max(Covid_Net_Sentiment)) |> 
  mutate(Delta_Net_COVID_Sentiment=Max_Net_COVID_Sentiment - Min_Net_COVID_Sentiment) |> 
  arrange(desc(Delta_Net_COVID_Sentiment))
#  arrange(desc(ticker)) |> 
#    arrange(Day_of_EarningsCall) 

Min_Max_Net_COVID_Sentiments  

```





Find top firms with the largest Deltas in their Net COVID Sentiments over time.


```{r}

# Top_Firms <- Min_Max_Net_COVID_Sentiments  |> 
#                   distinct(company_name)  
# Top_Firms

# write_csv(Top_Firms, '../data/Top_Firms.csv')


```
```{r}

# Dates_Min_Max_Net_COVID_Sentiments <- Min_Max_Net_COVID_Sentiments |> 
#           group_by(company_name) |> 
#           filter(Covid_Net_Sentiment==Min_Net_COVID_Sentiment | Covid_Net_Sentiment==Max_Net_COVID_Sentiment) |> 
#           arrange(desc(Delta_Net_COVID_Sentiment))
# 
# Dates_Min_Max_Net_COVID_Sentiments


# write_csv(Dates_Min_Max_Net_COVID_Sentiments, '../data/Dates_Min_Max_Net_COVID_Sentiments.csv')

```


Find unique ticker symbols:

```{r}
# Tickers <- Dates_Min_Max_Net_COVID_Sentiments |> 
#   group_by(company_name) |> 
#   distinct(ticker)
```


```{r}
# US_Tickers <- read_csv('../data/DescendingUSTickers_Extended.csv') 
# 
# US_Tickers <- US_Tickers |> 
#                   distinct(ticker)

# write_csv(US_Tickers, '../data/US_Tickers.csv')

```



Insert industry info via join:

```{r}

# Industries <- read_csv('../data/CompanyName_Ticker_Industry.csv')
# Industries

```
```{r}

# Industries <- Industries |> 
#                 select(-ticker)
# Industries

```

```{r}

# Net_COVID_Sentiments_Industries <- Min_Max_Net_COVID_Sentiments |> 
#     inner_join(Industries, by=join_by(company_name))
# 
# Net_COVID_Sentiments_Industries

```

Exporting data for fetching of share price data:
Arranging tickers by descending order in order to place the entries without tickers at the end

```{r}

# SharePrice_Write_CSV_Prep <- Net_COVID_Sentiments_Industries |>
#   arrange(desc(ticker)) |> 
#   arrange(desc(Industry))
# 
# write_csv(SharePrice_Write_CSV_Prep, "../data/Descending_Ticker_Industry.csv")

```




```{r}
Closing_Share_Price_Across_Time_AllYears <- read_csv('../data/Descending_Ticker_Industry_SharePrice.csv')

Closing_Share_Price_Across_Time  <- Closing_Share_Price_Across_Time_AllYears |> filter(Day_of_EarningsCall > 2019-12-31)
Closing_Share_Price_Across_Time
```


```{r}
# Closing_Share_Price_Across_Time_dates <- Closing_Share_Price_Across_Time |> mutate(date_earningscall=dmy(date_earningscall)) 
# Closing_Share_Price_Across_Time_dates

```




Examines Net COVID Sentiment across industries over time: 

Side note: Advertising Agencies is the reference Industry 

```{r}

lm(log(Covid_Net_Sentiment) ~ c(Industry) + Day_of_EarningsCall + Covid_Exposure, data=Closing_Share_Price_Across_Time) |> 
  summary()

```





Examines Positive COVID Sentiment across industries over time:

```{r}

lm(Covid_Pos_Sentiment ~ c(Industry) + Day_of_EarningsCall + Covid_Exposure, data=Closing_Share_Price_Across_Time) |> 
  summary()

```

```{r}

lm(Covid_Neg_Sentiment ~ c(Industry) + Day_of_EarningsCall + Covid_Exposure + PRiskT_health, data=Closing_Share_Price_Across_Time) |> 
  summary()

``` 


Examines Negative COVID Sentiment across industries over time:

```{r}

lm(Covid_Neg_Sentiment ~ c(Industry) + Day_of_EarningsCall + Covid_Exposure + PRiskT_health, data=Closing_Share_Price_Across_Time) |> 
  summary()

```




```{r}

lm(Percent_Change_bt_DayBefore_y_DayAfter ~ c(Industry) + Day_of_EarningsCall + Covid_Net_Sentiment + Covid_Net_Sentiment:c(Industry), data=Closing_Share_Price_Across_Time) |> 
  summary()

```

```{r}

PercentChange_SharePrices_HierchicalIndustryCompany_RandomIndustryFirms <- glmer(
  "Percent_Change_bt_DayBefore_y_DayAfter ~ Day_of_EarningsCall + Covid_Net_Sentiment + (1 | Industry/company_name)", 
  data=Closing_Share_Price_Across_Time,
  family=gaussian) 

PercentChange_SharePrices_HierchicalIndustryCompany_RandomIndustryFirms 
``` 

```{r}
summary(PercentChange_SharePrices_HierchicalIndustryCompany_RandomIndustryFirms)$coefficients  
```
p-value for Day_of_EarningsCall < 0.05
p-value for Covid_Net_Sentiment < 0.01

```{r}
tidy(PercentChange_SharePrices_HierchicalIndustryCompany_RandomIndustryFirms)
```


```{r}

PercentChange_SharePrices_HierchicalIndustryCompany <- glmer(
  "Percent_Change_bt_DayBefore_y_DayAfter ~ -1 + Day_of_EarningsCall + c(Industry) + Covid_Net_Sentiment:c(Industry) + (1 | company_name)", 
  data=Closing_Share_Price_Across_Time,
  family=gaussian) 

summary(PercentChange_SharePrices_HierchicalIndustryCompany)$coefficients  

``` 


```{r}

PercentChange_GeneralSentiment_SharePrices_HierchicalIndustryCompany <- glmer(
  "Percent_Change_bt_DayBefore_y_DayAfter ~ -1 + Day_of_EarningsCall + c(Industry) + Covid_Net_Sentiment:c(Industry) + Sentiment:c(Industry) + (1 | company_name)", 
  data=Closing_Share_Price_Across_Time,
  family=gaussian) 

summary(PercentChange_GeneralSentiment_SharePrices_HierchicalIndustryCompany)$coefficients  

``` 
```{r}

saveRDS(PercentChange_SharePrices_HierchicalIndustryCompany, file="../data/MixedEffects_HierarchicalModel.RDS")

```


```{r}
summary(PercentChange_SharePrices_HierchicalIndustryCompany)$coefficientsp[,4]  
```



```{r}
tidy(PercentChange_SharePrices_HierchicalIndustryCompany, conf.int=TRUE)
```

```{r}
FixedEffects_IndustryCoefficients <- tidy(PercentChange_SharePrices_HierchicalIndustryCompany, conf.int=TRUE) |> 
  filter(effect=="fixed")  

FixedEffects_IndustryCoefficients
```


```{r}
StatSig_Industries_Time_y_InteractionTermIndustryNetCOVIDSentiment <- FixedEffects_IndustryCoefficients |> 
  filter(conf.high < 0 | conf.low > 0)  

StatSig_Industries_Time_y_InteractionTermIndustryNetCOVIDSentiment
```








```{r}
tidy(PercentChange_SharePrices_HierchicalIndustryCompany, conf.int=TRUE) |> 
  filter(effect=="fixed") |> 
  ggplot(aes(x=reorder(term, estimate), y=estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high, width=0.05)) +
  labs(x="Industries") + 
  labs(y="% Change in Share Price as A Function of Net COVID Sentiment") +
  coord_flip() 
```
```{r}
Closing_Share_Price_Across_Time_DropNA <- Closing_Share_Price_Across_Time |> drop_na(`Percent_Change_bt_DayBefore_y_DayAfter`, `Industry`, `Day_of_EarningsCall`, `company_name`, `Covid_Net_Sentiment`)

Closing_Share_Price_Across_Time_DropNA
```


```{r} 
tibble(resid=resid(PercentChange_SharePrices_HierchicalIndustryCompany), date=Closing_Share_Price_Across_Time_DropNA$Day_of_EarningsCall) |> 
  filter(date > "2019-01-01") |> 
  ggplot(aes(x=date, y=resid)) +
  geom_point(alpha=0.2) +
  geom_smooth() +
  ylim(-25, 25)
# stat_poly_eq(use_label(c("eq", "adj.R2", "f", "p", "n")), vstep=22, size=3.8) 
```




```{r} 

BarGraph_StatSig_Industries <- ggplot(data=StatSig_Industries_Time_y_InteractionTermIndustryNetCOVIDSentiment, aes(x=reorder(term, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Industries") + 
  labs(y="% Change in Stock Price as A Function of Net COVID Sentiment") + 
  labs(title="Notable Industries Whose Share Prices Outperformed", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

BarGraph_StatSig_Industries

```


```{r}

Underscore_Removal = function(lab) {
  str_replace(lab, "_", " ") |> str_to_title()
}

cIndustry_Removal = function(lab) {
  str_remove(lab, "c(Industry)")  
}

DayOfEarningsCall_Removal = function(lab) {
  str_remove(lab, "Day_of_EarningsCall")  
}

BarGraph_StatSig_Industries$term <- BarGraph_StatSig_Industries$term |>
                                      map(Underscore_Removal)

BarGraph_StatSig_Industries$term <- BarGraph_StatSig_Industries$term |> 
                                      map(cIndustry_Removal) 

BarGraph_StatSig_Industries$term <- BarGraph_StatSig_Industries$term |> 
                                      map(DayOfEarningsCall_Removal)

BarGraph_StatSig_Industries

```

```{r}
StatSig_IndustryNetCOVIDSentimentInteraction <- StatSig_Industries_Time_y_InteractionTermIndustryNetCOVIDSentiment |> filter(str_detect(term, ":Covid_Net_Sentiment"))
StatSig_IndustryNetCOVIDSentimentInteraction
```
 
```{r}
StatSig_Industries <- StatSig_Industries_Time_y_InteractionTermIndustryNetCOVIDSentiment |> filter(!str_detect(term, ":Covid_Net_Sentiment"))
StatSig_Industries
``` 


```{r}

BarGraph_StatSig_IndustryNetCOVIDSentimentInteraction <- ggplot(data=StatSig_IndustryNetCOVIDSentimentInteraction, aes(x=reorder(term, estimate), y=estimate)) +
                                                          geom_bar(stat="identity", fill="steelblue") +
                                                          coord_flip() +
                                                          theme_minimal() +
                                                          labs(x="Industries") + 
                                                          labs(y="% Change in Stock Price as A Function of Net COVID Sentiment") + 
                                                          labs(title="Industries Whose Stock Price Changes Disproportionally Correlate with Net COVID Sentiment", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

BarGraph_StatSig_IndustryNetCOVIDSentimentInteraction


```

```{r}

Str_Remove_Covid_Net_Sentiment = function(lab) {
  str_remove(lab, ":Covid_Net_Sentiment")  
}

BarGraph_StatSig_IndustryNetCOVIDSentimentInteraction$term <- BarGraph_StatSig_IndustryNetCOVIDSentimentInteraction$term |>
                                      map(Str_Remove_Covid_Net_Sentiment)

BarGraph_StatSig_IndustryNetCOVIDSentimentInteraction

```




```{r}

BarGraph_StatSig_Industries <- ggplot(data=StatSig_Industries, aes(x=reorder(term, estimate), y=estimate)) +
                                                          geom_bar(stat="identity", fill="steelblue") +
                                                          coord_flip() +
                                                          theme_minimal() +
                                                          labs(x="Industries") + 
                                                          labs(y="% Change in Stock Price as A Function of Net COVID Sentiment") + 
                                                          labs(title="Industries Whose Stock Price Changes Statistically Significantly Correlate with Net COVID Sentiment", subtitle="Mixed-Effect Linear Regression Analysis of How Changes in Stock Price Correlate with Net COVID-Related Sentiment")

BarGraph_StatSig_Industries


```




```{r}
tidy(PercentChange_SharePrices_HierchicalIndustryCompany, effects="ran_vals", conf.int=TRUE) 
```


```{r}
Random_Effect_Coeff_Desc <- tidy(PercentChange_SharePrices_HierchicalIndustryCompany, effects="ran_vals", conf.int=TRUE) |> arrange(desc(estimate))
Random_Effect_Coeff_Desc 
```

```{r}
Company_Industry  <- Closing_Share_Price_Across_Time |> 
  select(company_name, Industry) |> 
  unique()

Company_Industry 
```


```{r}
Firm_Industry_Random_Effect_Coeff_Desc <- Random_Effect_Coeff_Desc  |> 
  inner_join(Company_Industry, by=join_by(level==company_name))

Firm_Industry_Random_Effect_Coeff_Desc
```

Let's look at stock performance of firms within industries whose share price changes were less impacted by Net COVID Sentiment.

```{r}
Grocery_Stores <- ggplot(data=Firm_Industry_Random_Effect_Coeff_Desc |> filter(Industry=="Grocery Stores"), aes(x=reorder(level, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Companies") + 
  labs(y="Additional % of Correlative Change in Stock Price from Industry Average") + 
  labs(title="Changes in Stock Prices of Grocery Stores with Respect to Industry", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

Grocery_Stores
```



```{r}
Auto_n_Truck_Dealerships <- ggplot(data=Firm_Industry_Random_Effect_Coeff_Desc |> filter(Industry=="Auto & Truck Dealerships"), aes(x=reorder(level, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Companies") + 
  labs(y="Additional % of Correlative Change in Stock Price from Industry Average") + 
  labs(title="Changes in Stock Prices of Auto/Truck Dealership Firms with Respect to Industry", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

Auto_n_Truck_Dealerships
```

```{r}
Industrial_Distribution <- ggplot(data=Firm_Industry_Random_Effect_Coeff_Desc |> filter(Industry=="Industrial Distribution"), aes(x=reorder(level, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Companies") + 
  labs(y="Additional % of Correlative Change in Stock Price from Industry Average") + 
  labs(title="Changes in Stock Prices of Industrial Distribution Firms with Respect to Industry", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

Industrial_Distribution
```


Then, let's look at stock performance of firms within industries whose share price changes were more impacted by Net COVID Sentiment.



```{r}
Discount_Stores <- ggplot(data=Firm_Industry_Random_Effect_Coeff_Desc |> filter(Industry=="Discount Stores"), aes(x=reorder(level, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Companies") + 
  labs(y="Additional % of Correlative Change in Stock Price from Industry Average") + 
  labs(title="Changes in Stock Prices of Discount Stores with Respect to Industry", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

Discount_Stores
```


```{r}
Consumer_Electronics <- ggplot(data=Firm_Industry_Random_Effect_Coeff_Desc |> filter(Industry=="Consumer Electronics"), aes(x=reorder(level, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Companies") + 
  labs(y="Additional % of Correlative Change in Stock Price from Industry Average") + 
  labs(title="Changes in Stock Prices of Consumer Electronics Firms with Respect to Industry", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

Consumer_Electronics 
```

```{r}
Integrated_Freight_n_Logistics <- ggplot(data=Firm_Industry_Random_Effect_Coeff_Desc |> filter(Industry=="Integrated Freight & Logistics"), aes(x=reorder(level, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Companies") + 
  labs(y="Additional % of Correlative Change in Stock Price from Industry Average") + 
  labs(title="Changes in Stock Prices of Integrated Freight & Logistics Firms with Respect to Industry", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

Integrated_Freight_n_Logistics
```



Next, let's look into notable industries whose share prices outperformed those in other industries:



```{r}
Electronic_Gaming_n_Multimedia <- ggplot(data=Firm_Industry_Random_Effect_Coeff_Desc |> filter(Industry=="Electronic Gaming & Multimedia"), aes(x=reorder(level, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Companies") + 
  labs(y="Additional % of Correlative Change in Stock Price from Industry Average") + 
  labs(title="Changes in Stock Prices of Electronic Gaming & Multimedia Firms with Respect to Industry", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

Electronic_Gaming_n_Multimedia
```




```{r}
TopFirms <- Random_Effect_Coeff_Desc |> 
  filter(conf.low > 0)
TopFirms
```

```{r}
BottomFirms <- Random_Effect_Coeff_Desc |> 
  filter(conf.high < 0)
BottomFirms 
```


```{r}
StatSig_Firms <- Random_Effect_Coeff_Desc |> 
  filter(conf.high < 0 | conf.low > 0)
StatSig_Firms 
```


```{r}
Top20Firms <- Random_Effect_Coeff_Desc |> head(20) 
Top20Firms
```


Add a boolean statistical significance column:

```{r}

Firm_Industry_Random_Effect_Coeff_Desc_StatSig <- Random_Effect_Coeff_Desc  |> 
  inner_join(Company_Industry, by=join_by(level==company_name)) |> 
  select(level, estimate, conf.low, conf.high, Industry) |> 
  filter(conf.high < 0 | conf.low > 0) |> 
  mutate(`Statistically Significant?`="Yes")

Firm_Industry_Random_Effect_Coeff_Desc_StatSig
```


```{r}

Firm_Industry_Random_Effect_Coeff_Desc_StatInsig <- Random_Effect_Coeff_Desc  |> 
  inner_join(Company_Industry, by=join_by(level==company_name)) |> 
  select(level, estimate, conf.low, conf.high, Industry) |> 
  filter(conf.high > 0 & conf.low < 0) |> 
  mutate(`Statistically Significant?`="No")

Firm_Industry_Random_Effect_Coeff_Desc_StatInsig
```


Piecing the firms whose stats are statistically significant back together with those whose stats aren't:


```{r}
Firm_Industry_Random_Effect_Coeff_Desc_StatSig_y_StatInsig <- bind_rows(Firm_Industry_Random_Effect_Coeff_Desc_StatSig, Firm_Industry_Random_Effect_Coeff_Desc_StatInsig)

Firm_Industry_Random_Effect_Coeff_Desc_StatSig_y_StatInsig
```




```{r} 
BarGraph_AllFirms <- ggplot(data=Random_Effect_Coeff_Desc, aes(x=reorder(level, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Companies") + 
  labs(y="% of Additional Correlative Change in Stock Price from Industry Average") + 
  labs(title="Stellar Companies Whose Share Prices Outperformed Those in Their Respective Industries", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

BarGraph_AllFirms 
```


```{r}
BarGraph_StatSig_Firms <- ggplot(data=StatSig_Firms, aes(x=reorder(level, estimate), y=estimate)) +
  geom_bar(stat="identity", fill="steelblue") +
  coord_flip() +
  theme_minimal() +
  labs(x="Companies") + 
  labs(y="Additional % of Correlative Change in Stock Price from Industrial Average") + 
  labs(title="Notable Companies Whose Correlational Performance Exceeded Their Respective Industry", subtitle="Mixed-Effect Linear Regression Analysis of How Percentage Change in Share Price Correlates with Net COVID-Related Sentiment")

BarGraph_StatSig_Firms
```
```{r}
select_company=c("Carmax Inc")

Closing_Share_Price_Across_Time_DropNA_highlight <- Closing_Share_Price_Across_Time_DropNA |> 
  mutate(highlight=case_when(company_name %in% select_company ~ TRUE,
                               .default=FALSE))
```


```{r}

Closing_Share_Price_Across_Time_DropNA_highlight |> 
  filter(Industry==Industry[(Closing_Share_Price_Across_Time_DropNA_highlight$company_name=="Lovesac Co")]) |> 
  ggplot(aes(x=Day_of_EarningsCall, y=Percent_Change_bt_DayBefore_y_DayAfter)) +
  geom_point(aes(size=Covid_Net_Sentiment, color=highlight), alpha=0.7, show.legend=FALSE) +
  geom_smooth(method=lm, formula=y ~ x) + 
  scale_color_manual(values=c("orange", "black")) +
  # scale_size_manual(values=c(1, 3)) +
  # geom_label_repel(data=Closing_Share_Price_Across_Time_DropNA_highlight |> filter(highlight==TRUE), aes(label=company_name)) +
  stat_poly_eq(use_label(c("eq", "adj.R2", "f", "p", "n")), vstep=22, size=3.8) 

```



```{r}
# vcov(PercentChange_SharePrices_HierchicalIndustryCompany)
```

```{r} 

PercentChange_SharePrices_HierchicalIndustryCompany <- lmer(Percent_Change_bt_DayBefore_y_DayAfter ~ Day_of_EarningsCall + Covid_Neg_Sentiment + c(Industry) + Covid_Neg_Sentiment:c(Industry) + (1 | company_name), data=Closing_Share_Price_Across_Time) 

summary(PercentChange_SharePrices_HierchicalIndustryCompany)  

```


```{r} 

PercentChange_SharePrices_HierchicalIndustryCompany <- lmer(Percent_Change_bt_DayBefore_y_DayAfter ~ Day_of_EarningsCall + Covid_Pos_Sentiment + c(Industry) + Covid_Pos_Sentiment:c(Industry) + (1 | company_name), data=Closing_Share_Price_Across_Time) 

summary(PercentChange_SharePrices_HierchicalIndustryCompany)  

```



```{r}

lm(Percent_Change_bt_DayBefore_y_DayAfter ~ c(Industry) + Day_of_EarningsCall + Covid_Exposure + Covid_Pos_Sentiment + Covid_Pos_Sentiment:c(Industry), data=Closing_Share_Price_Across_Time) |> 
  summary()

```


```{r}

lm(Percent_Change_bt_DayBefore_y_DayAfter ~ c(Industry) + Day_of_EarningsCall + Covid_Neg_Sentiment + Covid_Neg_Sentiment:c(Industry), data=Closing_Share_Price_Across_Time) |> 
  summary()

```







